{{module}} Analysis

### 2024-03-18 templates/analysis-module-R/notebook-template.Rmd
Get fancy with handlebars

---
title: Analysis Title
author:
  - Your name here
date: "`r Sys.Date()`"
output: html_notebook
---

@@

# This module's base path, found by the presence of an `renv` directory
module_base <- rprojroot::find_root(rprojroot::is_renv_project)
# If you are not using `renv`, you might use something like the following instead:
# module_base <- file.path(repository_base, "analyses", "{module_name}")
```

>>>>

---
title: "{{module}} Analysis"
author:
  - Your name here
date: "`r Sys.Date()`"
output: html_notebook
---

@@

# The path to this module
module_base <- file.path(repository_base, "analyses", "{{module}}")
# If you are using `renv`, you might use something like the following instead:
# module_base <- rprojroot::find_root(rprojroot::is_renv_project)
```
